### 2025-06-20 manuscripts/09-JERP-v2/submit_journal-main.tex
.....

    \begin{spacing}{\rrxspc}
        Thank you for these important methodological points. Regarding the generated regressor issue: The parental characteristics are included solely as controls and not for inference purposes. I do not interpret these coefficients, as my primary interest lies in $\beta_1$, which captures the gap between Hispanic and White last names. Since I am only using these synthetic characteristics as controls and not making inference about their coefficients, this should not affect the standard errors or p-values of my coefficient of interest $\beta_1$, which is not a generated regressor.
    \end{spacing}

>>>>

    \begin{spacing}{\rrxspc}
        I am grateful to the referee for raising this important concern. I have expanded the discussion of these methodological issues in the empirical approach section. Regarding the generated regressor issue, I updated the regression results in the manuscript with results that do not include the specification where ‘synthetic parents‘ are included in the controls. This alleviates the concern regarding generated, as they are no longer in the regression.
    \end{spacing}
